Sets

### 2023-10-01 rec06/paper.tex
comprehension

\begin{eg}
  The empty set is a subset of any set.
\end{eg}
\begin{proof}
  Let $y$ be any set.
  By definition, $\varnothing \subseteq y \cng \forall z.(z \in \varnothing \imp z \in y)$.
  Let $z$ be given.
  Assume that $z \in \varnothing$.
  This allows us to derive a contradiction since $z \notin \varnothing$.\footnote{This is not a proof by contradiction, but let's ignore the details for now.}
\end{proof}

@@

@@

>>>>

\begin{lem}
  The empty set is a subset of any set.
  \[
    \forall y.\,\varnothing \subseteq y
  \]
\end{lem}
\begin{proof}
  Let $y$ be any set.
  By definition, $\varnothing \subseteq y \cng \forall z.(z \in \varnothing \imp z \in y)$.
  Let $z$ be given.
  Assume that $z \in \varnothing$, but this is impossible since $z \notin \varnothing$.\footnote{This is not a proof by contradiction, but let's ignore the details for now.}
\end{proof}

\begin{lem}
  Every set is a subset of itself.
\end{lem}
\begin{proof}
  Exercise.
\end{proof}

@@

\begin{eg}
  \begin{enumerate}
  \item[]
  \item $\{a,b,c,d,d\} = \{a,b,c,d\}$.
  \item $\{a,b,c\} = \{c,b,a\}$.
  \end{enumerate}
\end{eg}

@@

\subsection{Set Difference}
\label{sec:set-difference}
